---
title: "Sensitivity Analysis - Latin Hypercube Sampling"
author: "Group H - Paloma Cartwright, Juliet Cohen, Julia Parish"
date: '2022-04-26'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(here)
library(SciViews) # ln() function
library(pse)
library(purrr)
```

# Sensitivity Analysis - Latin Hypercube Sampling


This environmental model was completed as an assignment for the course, Environmental Data Science 230 | Environmental Science & Management: Modeling Environmental Systems. The goal of this assignment was to code a function to compute atmosphere condcuctance and to conduct a formal sensitivity analysis using the Latin Hypercube Sampling (LHS) random sampling method. This assignment focuses on developing skills to create a atmospheric conductance model function, utilize the Latin Hypercube Sampling to generate near random sample of parameter values, and then plot the atmospheric conductance values.

## 1. Code a function to compute atmospheric conductance

```{r model}
source(here("R/atmcon.R"))
```

## 2. Run `atmcon` model and provide a single estimate of atmospheric conductance for this forest.  

```{r run model}
ac_forest <- atmcon(vm = 250, h = 1000)
ac_forest

ac_forest_rounded <- round(ac_forest[[1]], 2)

print(paste0("The atmospheric conductance for this vegetation is ", 
             ac_forest_rounded, " centimeters per second."))
```

## 3. Conduct a sensitivity analysis
Consider the sensitivity of estimates to uncertainty in the following parameters and inputs:

- *h*
- *kd*
- *k0*
- *v*

### 3.A Use LHS to generate parameter values for the 4 parameters
```{r lHS}
# define 4 parameters to test
factors = c("vm", "h", "kd", "k")

#define sample size
nsets = 100

# set distributions for defined parameters
# qnorm=windspeed, qunif=height, qnorm=k, qnorm=k0
q = c("qnorm", "qunif", "qnorm", "qnorm")

q.arg = list(list(mean = 250, sd = 30), #windspeed
             list(min = 950, max = 1050), #height
             list(mean = 0.7, sd = 0.07), #k
             list(mean = 0.1, sd = 0.01)) #k0
q.arg

# run LHS and generate samples
sens_ac = LHS(NULL, factors, nsets, q, q.arg)
#sens_ac
#summary(sens_ac)
#sens_ac$data
# NULL indicates there is no model

sens_pars <- get.data(sens_ac)
head(sens_pars)
```

### 3.B Run the atmospheric conductance model, `atmcon`, for LHS derived parameters and return aerodynamic conductances

```{r}
source(here("R/atmcon.R"))

ac_lhs <- pmap(sens_pars, atmcon)
head(ac_lhs[[2]])
```


```{r}
atmospheric_conductances <- ac_lhs %>% 
  map_dfr(`[`, "ac")

atmospheric_conductances
```

### 3.C. Plot conductance estimates in a way that accounts for parameter uncertainty

```{r, fig.cap= "This boxplot shows distribution of atmospheric conducances with given forest parameters"}
#data <- atmospheric_conductances %>% 
#  gather(value = "value", key = )

ggplot(data = atmospheric_conductances, aes(y = ac)) +
  geom_boxplot() +
  labs(y = "Atmospheric Conductance cm/s",
       title = "Forest Atmospheric Conductance") +
  theme_minimal() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) 
  
```

### 3.D. Plot conductance estimates against each of your parameters

```{r}
#pse::plotscatter(sens_ac)
```

### 3.E. Estimate the Partial Rank Correlation Coefficients (PRCC)

```{r}

```


### 3.F. Discussion

#### What do the results tell about how aerodynamic conductance? 

#### What does it suggest about what you should focus on if you want to reduce uncertainty in aerodymaic conductance estimates? 

#### Does this tell you anything about the sensitivity of plant water use to climate change?





